%-------------------------
% Resume in LaTeX
% Author: Vardh Chhajer
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{geometry}

\geometry{
  letterpaper,
  top=0.5in,
  bottom=0.5in,
  left=0.55in,
  right=0.55in
}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%---------- HEADING ----------
\begin{center}
    {\Huge \scshape Vardh Chhajer} \\ \vspace{4pt}
    \small
    +91-9571156569 $|$
    \href{mailto:chhajervardh@gmail.com}{\underline{chhajervardh@gmail.com}} $|$
    \href{https://linkedin.com/in/vardh}{\underline{linkedin.com/in/vardh}} $|$
    \href{https://github.com/membranegaming}{\underline{github.com/membranegaming}}
\end{center}

%---------- SUMMARY ----------
\section{Summary}
Computer science student who enjoys building simple, user-friendly software systems. Interested in working with Artificial Intelligence and exploring how technology can be applied to real-world problems. Also curious about Web3, finance, and businesses.

%---------- EDUCATION ----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SVKM's SBMP Polytechnic College}{India}
      {Diploma in Computer Science}{2023 -- Present}
  \resumeSubHeadingListEnd

%---------- TECHNICAL SKILLS ----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C\#, SQL, TypeScript, Kotlin} \\
     \textbf{Frameworks \& Tools}{: .NET Framework, Visual Studio, Streamlit, React, Vite, FastAPI, Tailwind CSS, Android Studio} \\
     \textbf{Databases}{: MSSQL, SQLite} \\
     \textbf{Systems}{: Linux, Docker, WSL, Networking} \\
     \textbf{AI \& Blockchain}{: LLM APIs, Speech-to-Text, Smart Contracts}
    }}
 \end{itemize}

%---------- EXPERIENCE ----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {DeepCytes Cyber Labs}{Remote}
      {Cyber Analyst}{May 2026 -- Jun 2026}
      \resumeItemListStart
        \resumeItem{Performed cybersecurity analysis and threat assessment tasks in a fully remote capacity.}
        \resumeItem{Contributed to cyber intelligence operations and security research within a professional lab environment.}
      \resumeItemListEnd

    \resumeSubheading
      {Balar Fabrics Pvt. Ltd.}{Hybrid}
      {Software Development and Deployment Intern}{Jan 2026 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Parts Inventory System:} Built a full-stack Streamlit-based inventory management system with barcode scanning, SQLite backend, and TSPL thermal printer integration for a machinery parts store.}
        \resumeItem{\textbf{ERP Integration:} Implemented bulk data migration pipeline from Excel via Pandas/openpyxl and interactive dashboards with Plotly charts and CSV export.}
        \resumeItem{\textbf{Tech Stack:} Python, Streamlit, SQLite, Pandas, Plotly, pywin32, JavaScript.}
      \resumeItemListEnd

    \resumeSubheading
      {Balar Fabrics Pvt. Ltd.}{On-site}
      {Software Development Intern}{Nov 2024 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Inventory System:} Designed and deployed a barcode-based inventory management system used in production.}
        \resumeItem{\textbf{Tech Stack:} C\#, Visual Studio, .NET Framework, Microsoft SQL Server (MSSQL).}
        \resumeItem{\textbf{Networking:} Configured local networking and IP-based deployment in a live environment.}
      \resumeItemListEnd

    \resumeSubheading
      {Spectrum'25 College Techfest}{College Campus}
      {Technical Team Member}{2024}
      \resumeItemListStart
        \resumeItem{\textbf{Web Development:} Built and maintained the techfest website using React and Node.js.}
        \resumeItem{\textbf{Collaboration:} Provided on-ground technical support and coordinated with teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%---------- PROJECTS ----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Barcode-Based Inventory Management System (Python)} $|$ \emph{Industry-Oriented Project}}{}
          \resumeItemListStart
            \resumeItem{Built a Streamlit-based inventory management system with real-time barcode scanning, multi-page navigation, and SQLite backend for a machinery parts store.}
            \resumeItem{Designed a relational database schema (SQLite) with 6 normalized tables --- parties, items, machines, persons, parts inward, and parts usage --- with foreign key relationships and computed remaining quantities.}
            \resumeItem{Developed TSPL thermal printer integration (TSC TTP-244 Pro) via Windows Print Spooler (\texttt{pywin32}), generating Code 39 barcodes across a 3-column label grid with sub-millimeter alignment calibration.}
            \resumeItem{Engineered a global barcode scanner intercept using injected JavaScript that detects rapid keystroke patterns ($<$500ms) to distinguish scanner input from human typing, auto-redirecting to the usage page with pre-filled data.}
            \resumeItem{Implemented ERP master data migration pipeline --- bulk import of parties and items from Excel (\texttt{.xlsx}) via Pandas/openpyxl with full database reset capability.}
            \resumeItem{Created interactive dashboard with Plotly charts, CSV export, searchable records, and CRUD operations for inward entries and usage records.}
            \resumeItem{\textbf{Tech Stack:} Python, Streamlit, SQLite, Pandas, Plotly, TSPL/Code 39, JavaScript, pywin32, openpyxl.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Barcode-Based Inventory Management System} $|$ \emph{Industry-Oriented Project}}{}
          \resumeItemListStart
            \resumeItem{Built a barcode-based inventory system to manage stock movement and material records in a live environment.}
            \resumeItem{Deployed in production with barcode scanners and local network integration.}
            \resumeItem{\textbf{Tech Stack:} C\#, .NET Framework, Visual Studio, MSSQL.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{AI-Based Design Modelling for Textile Catalogs} $|$ \emph{Industry-Oriented Project}}{}
          \resumeItemListStart
            \resumeItem{Used AI models to modify and regenerate textile designs for catalog updates.}
            \resumeItem{Created a web tool allowing users to upload or paste images and download modified outputs.}
            \resumeItem{\textbf{Tech Stack:} HTML, CSS, JavaScript, AI Image Models, n8n, Google Drive API.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Finsakhi -- Financial Education Platform} $|$ \emph{Hackathon Project}}{}
          \resumeItemListStart
            \resumeItem{Multi-module application featuring financial education, assessments, investments, podcasts, and AI chatbot support.}
            \resumeItem{Python-based backend with modular routers for lessons, stories, and podcasts; React + Vite frontend for user engagement.}
            \resumeItem{\textbf{Tech Stack:} Python, React, Vite, FastAPI.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{HealthBridge -- Integrated Health Management Platform} $|$ \href{https://healthbridge.page}{\underline{healthbridge.page}}}{}
          \resumeItemListStart
            \resumeItem{Platform for blood report analysis, health tracking, meal planning, and AI-powered chat support.}
            \resumeItem{Python APIs with modular services for uploads, secure data storage, rate limiting, and AI-driven recommendations.}
            \resumeItem{\textbf{Tech Stack:} Python, React, Vite, Tailwind CSS.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Hides -- Secure File Storage Application} $|$ \href{https://hides.app}{\underline{hides.app}}}{}
          \resumeItemListStart
            \resumeItem{FastAPI backend with modular components for authentication, cryptography, email, and file storage.}
            \resumeItem{Static frontend with wordlist extraction and cryptographic testing scripts.}
            \resumeItem{\textbf{Tech Stack:} Python, FastAPI, HTML, CSS, JavaScript.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{StudyFlow -- Project \& Document Management App} $|$ \emph{Personal Project}}{}
          \resumeItemListStart
            \resumeItem{Web application for managing projects, document uploads, and study workflows with PDF export and database integration.}
            \resumeItem{Modular UI components, user settings with API key management, and context-driven state management.}
            \resumeItem{\textbf{Tech Stack:} React, TypeScript, Vite.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Secure Messaging Application (Matrix-Based)} $|$ \emph{Personal Project}}{}
          \resumeItemListStart
            \resumeItem{Deployed and configured a self-hosted Matrix server with built-in end-to-end encryption.}
            \resumeItem{\textbf{Tech Stack:} Linux, Matrix Server.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%---------- PROJECTS IN PROGRESS ----------
\section{Projects in Progress}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{SMS Forwarder Pro} $|$ \emph{Android Application -- Kotlin}}{}
          \resumeItemListStart
            \resumeItem{A lightweight, privacy-first Android SMS forwarder built to solve a real-world business problem: reliably delivering banking OTPs from a registered family business number without manual intervention.}
            \resumeItem{\textbf{Privacy \& Security:} Messages are forwarded directly from device to recipient with no third-party servers or intermediaries involved -- critical for sensitive banking communications.}
            \resumeItem{\textbf{Reliability:} Runs persistently as a foreground service, remaining fully functional when the app is closed or the screen is off -- addressing a core failure point of existing solutions.}
            \resumeItem{\textbf{Multi-Channel Forwarding:} Supports forwarding via SMS, Email, and Telegram, with customizable filters, local message logs, and per-rule configuration.}
            \resumeItem{Actively expanding with additional forwarding channels and features; designed for extensibility from the ground up.}
            \resumeItem{\textbf{Tech Stack:} Android Studio, Kotlin.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Jarvis -- Speech-to-Speech AI Assistant} $|$ \emph{Personal Project}}{}
          \resumeItemListStart
            \resumeItem{Speech-based AI assistant with conversational memory and natural voice responses.}
            \resumeItem{\textbf{Tech Stack:} Python, Streamlit, OpenAI Whisper, Google Gemini API.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Community Stablecoin System} $|$ \emph{Blockchain Project}}{}
          \resumeItemListStart
            \resumeItem{Developing a community-focused stablecoin using smart contracts on Solana and Algorand.}
            \resumeItem{\textbf{Tech Stack:} Solana, Algorand.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%---------- CERTIFICATIONS ----------
\section{Certifications}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Google Cybersecurity Professional Certificate}{Online}
      {Google}{2023}

    \resumeSubheading
      {SQL (Basic) Certificate}{Online}
      {HackerRank}{2025}

    \resumeSubheading
      {SQL (Advanced) Certificate}{Online}
      {HackerRank}{2025}

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
